### 2019-03-30 2_metg.tex
Tweaks to the paper.

METG(50\%) is the intersection of this curve with a vertical line through
Figure~\ref{fig:efficiency-mpi} at 50\% efficiency. In the figures, the red, dashed line shows the 50\% efficiency
level. At 50\% efficiency, MPI achieves an average task granularity of
4.6 us, thus the METG(50\%) of MPI is 4.6 us for this configuration of
the application. We use 50\% because it is a reasonable level of
efficiency in practice. Lower values would likely not be reasonable,
because operators of computing facilities prefer higher levels of
utilization. Values above 90\% can misrepresent the performance of
some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

METG is an appealing metric in part because it has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to show at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes dominated by overhead. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is the shape of
the METG curve.

@@

The METG metric has another useful property. Because METG is measured ``in place'' (i.e.,
without changing the number of nodes or cores available to the
application), METG isolates effects that are
due to shrinking problem size from effects that are due to
increased communication and other resource issues as
progressively larger portions of the machine are used.

Section~\ref{sec:evaluation} contains a comprehensive evaluation of
METG including how it changes with node count for a wide variety of
programming systems.

>>>>

METG(50\%) is the intersection of this curve with a vertical line through
Figure~\ref{fig:efficiency-mpi} at 50\% efficiency. In the figures, the red, dashed line shows the 50\% efficiency
level. At 50\% efficiency, MPI achieves an average task granularity of
4.6 us, thus the METG(50\%) of MPI is 4.6 us for this configuration of
Task Bench. We use 50\% because it is a reasonable level of
efficiency in practice. Lower values would likely not be reasonable,
because operators of computing facilities prefer higher levels of
utilization. Values above 90\% can misrepresent the performance of
some systems (see
Section~\ref{subsec:peak-performance-and-efficiency}).

METG is an appealing metric in part because it has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes dominated by overhead. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is the shape of
the METG curve.

@@

The METG metric has another useful property. Because METG is measured ``in place'' (i.e.,
without changing the number of nodes or cores available to the
application), METG isolates effects that are
due to shrinking problem size from effects that are due to
increased communication and other resource issues as
progressively larger portions of the machine are used. Section~\ref{sec:evaluation} contains a comprehensive evaluation of
METG including how it changes with node count for a wide variety of
programming systems.

### 2019-03-30 3_task_bench.tex
Tweaks to the paper.

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The core aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all cases, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner, and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

>>>>

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The core aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner, and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

### 2019-03-30 4_implementation.tex
Tweaks to the paper.

Chapel~\cite{Chapel15} is an explicitly parallel programming language
that follows a \emph{multi-resolution} approach to parallel
programming, with support for parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), data distributions, tasks, and
synchronization primitives, and array promotion. For Task Bench, we decided to target a low-level implementation in
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization.

@@

Data in PaRSEC is stored in a built-in matrix data structure with a 2D
block cyclic distribution.  The Task Bench implementation divides this
matrix into $M$ by $N$ tiles where $N$ equals to the width of the task
graph and $M$ varies from 2 to the height of the task graph depending
on optimizations performed to alleviate write-after-read dependencies.
Tiles are distributed across nodes in pre-defined patterns,
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent sets of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

>>>>

Chapel~\cite{Chapel15} is a programming language
that follows a \emph{multi-res\-o\-lu\-tion} approach to parallel
programming, with support for parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), data distributions, tasks,
synchronization primitives, and array promotion. For Task Bench, we decided to target a low-level implementation in
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization.

@@

Data in PaRSEC is stored in a built-in matrix data structure with a 2D
block cyclic distribution. Tiles of the matrix are distributed across nodes in pre-defined patterns,
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent sets of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

### 2019-03-30 e6_communication.tex
Tweak captions.
More text in evaluation.
More text for evaluation section.
More text for section 5.
Tweak spacing around figure captions.
Tweaks to the paper.

\begin{figure*}[t]

@@

\subfloat[4096 bytes per task dependency.\label{fig:efficiency-communication-16}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_4096.pdf}
}
\subfloat[65536 bytes per task dependency.\label{fig:efficiency-communication-256}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_65536.pdf}
}

\caption{Task granularity vs efficiency for varying communication.\label{fig:metg-communication}}
\end{figure*}

>>>>

\begin{figure*}[t!]

@@

\subfloat[4096 bytes per task dependency.\label{fig:efficiency-communication-4096}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_4096.pdf}
}
\subfloat[65536 bytes per task dependency.\label{fig:efficiency-communication-65536}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_65536.pdf}
}

\vspace{-0.25cm}
\caption{Task granularity vs efficiency for varying communication (spread pattern, 5 dependencies per task, 4 task graphs, 64 nodes). Lower is better.\label{fig:efficiency-communication}}
\vspace{-0.05cm}
\end{figure*}
